\input{info/info.tex}
\geometry{left=1.4cm, top=1.4cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Fox Talent Acquisition Team}
  {Fox Networks Engineering \& Operations}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer Summer Internship}
% How the letter is opened
\letteropening{Dear Talent Acquisition Team,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Resume}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Jean C. Pe\~na~~~·~~~Cover Letter}
  {Attached: Resume}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am a Computer Science student at The City College of New York with a minor
in Psychology. I am interested in machine learning, penetration testing, video
game design, and education. I am currently learning about penetration testing
tools during my free time using Kali Linux. I am knowledgeable in C++, C\#,
Java, JavaScript, JQuery, HTML5, and CSS. Python is a new language that I am
becoming comfortable with.
%I've used VHDL in my Computer Organization course,
%Scheme in my current Programming Language Paradigms class, and Django for a
%project for Software Engineering last semester. I think LaTeX is amazing and I
%am currently transitioning from office tools to LaTeX.
\par
For Software Engineering, I worked in a group on an ebook sharing platform. My
team decided that Django was great for rapid prototyping, so we focused our
efforts with the Django framework and called our platform "EBShare".
For me, this was a completely new experience because it was the first time 
I have ever done anything with Python. Our platform was a website that was
designed using Bootstrap and all of the pages were rendered by Django.
\par
A current project that I am working on with the ACM club is a vertical
scrolling shoot em' up called Chapel Fighter. This is primarily written in
JavaScript. My small team is using Phaser because it is a great framework for
designing 2D games. Currently, the best experience is available on a PC's
web browser, although the game can be previewed on a mobile browser.
\par
A few of my projects use RESTful APIs such as NYC Open
Data(Socrata), Parse.com, Twilio, Clarifai, and Giphy. Recently, I attended
HackNY, a hackathon at New York University and used Twilio, Clarifai, and
Giphy with 3 other developers and created a phone menu system called SMSstuff,
primarily with Twilio. To make our project a little more interesting, we added
some Easter Eggs in a couple of menu paths. One of them grabbed a randomly
generated gif from Giphy and started a guessing game which asked the user to
guess any of the tags that Clarifai assigned to the gif.

\lettersection{Why Fox?}
At the NSBE career fair, I was given the impression that Fox is a top
competitor in many areas. It's a top competitor in sports and prime time
entertainment and has shown persistence and succeeded where other people had
doubted them. For example, prime time cartoons didn't seem plausible to
everyone else, and yet Fox has The Simpsons and Family Guy. (paraphrasing a
recruiter)
\par
Some of the things that are important to me in the work place include working
with and learning from intelligent people, continuous learning, networking,
solving important problems, becoming valuable to the company, and getting
educational support. I think these are things that would be fulfilled at Fox.

\lettersection{Why Me?}
I'm a great person to work with. I'm independent and a great team player. I'm always
looking for a way to learn, as my values show. I already have a great set of
skills that match up with the requirements, making me competent and
realistically capable of providing software solutions to meet Fox's needs. I'm
also looking to expand the number of frameworks that I use with
JavaScript. In a nutshell, I'm ready to hit the ground running and help exceed
Fox's expectations for success.
\par
I'm excited to learn more about the Software Engineer Summer Internship and
share how I would be a good fit for Fox. I hope to hear from you soon.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
